The Name of the Title is Hope

### 2023-12-13 input/6_results.tex
revision v1

\section{Results}
In the intentional binding task, i.e. the estimation of the time interval between tap and tone, participants generally underestimated the average real delay (350ms) in all three conditions (INTENTION M = 160.3, SD = 116; EXTERNAL M = 176.7, SD = 120.7, AUGMENTED M = 162.6, SD = 118.9). The condition influenced the estimation (${\chi^{2}_{(2)}} = 15.9, p < .001$). In EXTERNAL the estimation was higher compared to INTENTION (beta = 19.2, p < 0.001). Also in EXTERNAL, the estimation was higher compared to AUGMENTED (beta = 18.6, p < 0.001). No difference was observed between INTENTION and AUGMENTED.

@@

The subjective rating of control differed between conditions (${\chi^{2}_{(2)}} = 35.9, p < .001$). Post-hoc pairwise comparisons revealed that participants rated their motion control higher in INTENTION compared to EXTERNAL (beta = 4.9, p < .0001), and higher in INTENTION compared to AUGMENTED (beta = 3, p < .0001). Further, higher control was observed in AUGMENTED compared to EXTERNAL (beta = 1.9, p = .006).

@@

\subsection{Classifier Performance}
Visual inspection of the amplitudes at electrode Cz revealed an increase in the difference between \textit{pre-movement} and \textit{idle} data segments towards the onset of the finger movement, see figure~\ref{fig:EEG_results} a. The slope feature for the exemplary channel discriminates well between the two classes (${t_{(8)}} = 3.6, p = .003$), see figure ~\ref{fig:EEG_results} b bottom. The scalp maps in figure~\ref{fig:EEG_results} b top show the (color-coded) mean slope for each channel and for each class. Central channels on the contralateral side to the moving finger on the right hand show a negative slope for the pre-movement class and a neutral slope for the idle class. Furthermore, differences in slope can also be observed at frontal electrodes over the left hemisphere as well as parietal electrodes, were a positive slope manifests only for the idle class.

The grid-search over channels resulted in the BCI leveraging on average 11.5 (SD = 3.7) channels. Classifier cross-validation resulted in a mean F1 score of .7 (SD = .03), see figure~\ref{fig:EEG_results} c. We set the detection threshold to 15\% false positive rate and at that rate, observed a mean threshold of 57\% (SD = .02). Hence, on average, the classifier switched on the EMS when it predicted class \textit{pre-movement} with 57\% probability.
% TODO add percentage of trials the prototype was activated before touching the screen (SD = ?)

@@

Some participants reported that the stimulation ``sometimes overlapped with the movement, but not often,'' or, it ``came only rarely.'' Another one noted, ``In a few cases, the stimulation came when I had already started the movement.'' For several participants, this overlap between their actions and the system's response occurred infrequently, with another user noting, ``Once, in the millisecond range between my planned movement and its execution.'' However, for some participants, there were moments of near-perfect synchronization, as described by one participant, ``In 3 cases it happened that my intention to press and the impulse of the device happened simultaneously.'' Another one noted, ``Sometimes it really happened that they overlapped. So that I just started to move, and then the device activated,'' that user estimated an overlap of ``40\%'' while another said [we worked] ``15\% together.'' These accounts collectively highlight the varied and occasionally synchronous nature of the system's timing in relation to the users' intentions.

>>>>

\section{Results}
In the intentional binding task, i.e. the estimation of the time interval between tap and tone, participants generally underestimated the average real delay (350ms) in all three conditions (INTENTION M = 160.3, SD = 116; EXTERNAL M = 176.7, SD = 120.7, AUGMENTED M = 162.6, SD = 118.9). The condition influenced the estimation (${\chi^{2}_{(2)}} = 15.9, p < .001$). In EXTERNAL the underestimation was less pronounced compared to INTENTION ($beta = 19.2, p < 0.001$). This was also the case in EXTERNAL, with less pronounced underestimations of the time interval between tap and tone compared to AUGMENTED ($beta = 18.6, p < 0.001$). No difference was observed between INTENTION and AUGMENTED.

@@

The subjective rating of control differed between conditions (${\chi^{2}_{(2)}} = 35.9, p < .001$). Post-hoc pairwise comparisons revealed that participants rated their motion control higher in INTENTION compared to EXTERNAL ($beta = 4.9, p < .0001$), and higher in INTENTION compared to AUGMENTED ($beta = 3, p < .0001$). Further, higher control was observed in AUGMENTED compared to EXTERNAL ($beta = 1.9, p = .006$).

@@

\subsection{Classifier Performance}
Visual inspection of the amplitudes at electrode Cz revealed an increase in the difference between \textit{pre-movement} and \textit{idle} data segments towards the onset of the finger movement, see figure~\ref{fig:EEG_results} a. The slope feature for the exemplary channel discriminates well between the two classes (${t_{(8)}} = 3.6, p = .003$), see figure ~\ref{fig:EEG_results} b bottom. The scalp maps in figure~\ref{fig:EEG_results} b top show the (color-coded) mean slope for each channel and each class. Central channels on the contralateral side to the moving finger on the right hand show a negative slope for the pre-movement class and a neutral slope for the idle class. Furthermore, differences in slope were also observed at frontal electrodes over the left hemisphere as well as parietal electrodes, were a positive slope manifested only for the idle class.

The grid-search over channels resulted in the BCI leveraging on average 11.5 (SD = 3.7) channels. \textcolor{green}{Besides channels C3, C4, and Cz, that were always included, other common channels (retained for at least 3 participants) included FT9, AF3, F5, F7, F2, FT8, and AF7.} The classifier cross-validation resulted in a mean F1 score of .7 (SD = .03), see figure~\ref{fig:EEG_results} c. We set the detection threshold to 15 \% false positive rate and at that rate, observed a mean threshold of 57 \% (SD = .02). Hence, on average, the classifier switched on the EMS when it predicted class \textit{pre-movement} with 57 \% probability.
% TODO add percentage of trials the prototype was activated before touching the screen (SD = ?)

@@

Some participants reported that the stimulation ``sometimes overlapped with the movement, but not often,'' or, it ``came only rarely.'' Another one noted, ``In a few cases, the stimulation came when I had already started the movement.'' For several participants, this overlap between their actions and the system's response occurred infrequently, with another user noting, ``Once, in the millisecond range between my planned movement and its execution.'' However, for some participants, there were moments of near-perfect synchronization, as described by one participant, ``In 3 cases it happened that my intention to press and the impulse of the device happened simultaneously.'' Another one noted, ``Sometimes it really happened that they overlapped. So that I just started to move, and then the device activated,'' that user estimated an overlap of ``40 \%'' while another said [we worked] ``15 \% together.'' These accounts collectively highlight the varied and occasionally synchronous nature of the system's timing in relation to the users' intentions.
